|

### 2022-04-05 paper/paper.Rmd
title change

---
title: |
  A new simplified manual tour, with examples in mathematica
type: Short Technical Note
author:
  - name: Alex Aumann
    affil: a
    email: aaum0002@student.monash.edu
  - name: German Valencia
    affil: a
    email: german.valencia@monash.edu
  - name: Ursula Laa
    affil: b
    email: ursula.laa@boku.ac.at
  - name: Dianne Cook
    affil: c
    email: dicook@monash.edu
affiliation:
  - num: a
    address: |
      School of Physics and Astronomy, Monash University
  - num: b
    address: |
      Institute of Statistics, University of Natural Resources and Life Sciences, Vienna
  - num: b
    address: |
      Department of Econometrics and Business Statistics, Monash University
bibliography: biblio.bib
geometry: margin=2.5cm
abstract: |
  Something here
keywords: |
  data visualisation; grand tour; statistical computing; statistical graphics; multivariate data; dynamic graphics
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
  \usepackage{graphicx}
output: rticles::tf_article
keep_tex: true
---

>>>>

---
title: |
  A new simplified manual tour, with examples in mathematica and R
type: Short Technical Note
author:
  - name: Alex Aumann
    affil: a
    email: aaum0002@student.monash.edu
  - name: German Valencia
    affil: a
    email: german.valencia@monash.edu
  - name: Ursula Laa
    affil: b
    email: ursula.laa@boku.ac.at
  - name: Dianne Cook
    affil: c
    email: dicook@monash.edu
affiliation:
  - num: a
    address: |
      School of Physics and Astronomy, Monash University
  - num: b
    address: |
      Institute of Statistics, University of Natural Resources and Life Sciences, Vienna
  - num: b
    address: |
      Department of Econometrics and Business Statistics, Monash University
bibliography: biblio.bib
geometry: margin=2.5cm
abstract: |
  Something here
keywords: |
  data visualisation; grand tour; statistical computing; statistical graphics; multivariate data; dynamic graphics
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
  \usepackage{graphicx}
output: rticles::tf_article
keep_tex: true
---
